Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Avances

Afterwards, multi-objective unconstrained optimization is sought. All objective functions are minimized, and the points obtained as solution cannot be improved in a variable without harming, at least, another one. This last step is the most complete, giving more information of the behavior of the functions and the optimization process, but due to the greater complexity in the evaluation it is computed the last.

>>>>

Afterwards, multi-objective unconstrained optimization is sought. All objective functions are minimized, and the points obtained as solution contain a set of balanced optima which provide engineers with a valuable design tool. The results also give information about the evolution of the design variables along the Pareto front, which enables a better understanding of the energy-absorbing structures from a scientific point of view.
